%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Xiuquan Wang} % Your name
\address{\textbf{www:} https://xiuquan0418.github.io} % Your secondary addess (optional)
\address{\textbf{Office:} 500 W. County Lind Rd., K1, Tougaloo, MS 39174, U.S.} % Your address
\address{\textbf{Email:} xiuquan0418@gmail.com} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Professional Profile}
\begin{rSubsection}{}{}{}{}
\item[$\diamond$] Mathematician trained in partial differential equations with a broad knowledge base in numerical analysis and algorithms
%\item[$\diamond$] Trained in cardiovascular, renal, and endocrine physiology
\item[$\diamond$] In depth knowledge of mathematical modeling of physiological systems in an integrative setting 
\item[$\diamond$] Experienced programmer in Mathematica, HumMod/DES, R, Python, Matlab, Stata, LaTeX 
\end{rSubsection}
\end{rSection}




\begin{rSection}{Education}
%{\bf University of Mississippi Medical Center, Jackson, MS} \hfill {\em Jul. 2020} \\ 
%Investigator Training. in Data Science \smallskip\smallskip\\
{\bf Southern Illinois University, Carbondale, IL} \hfill {\em Aug. 2014} \\ 
Ph.D. in Mathematics \\
M.S. in Mathematics  \smallskip\smallskip\\
{\bf Hebei Normal University, China} \hfill {\em Aug. 2002} \\ 
B.S. in Electrical Engineering 
\end{rSection}

%%----------------------------------------------------------------------------------------
%%	Position SECTION
%%----------------------------------------------------------------------------------------
%
%\begin{rSection}{Professional Positions}
%
%{\bf Assistant Professor}, Department of Mathematics \& Computer Science, \hfill {\em Aug. 2015 - Present} \\ 
%Tougaloo College, Tougaloo, MS \smallskip\smallskip\\
%{\bf Investigator}, Mississippi Center for Clinical and Translational Research, \hfill {\em Jul. 2017 - Present} \\ 
%University of Mississippi Medical Center, Jackson, MS \smallskip\smallskip\\
%{\bf Adjunct Biostaistics Professor}, Jackson Heart Study (Tougaloo Campus), \hfill {\em Jan. 2018 - Present} \\ 
%Jackson, MS \smallskip\smallskip\\
%{\bf Assistant Professor}, Department of Mathematics \& Statistics, \hfill {\em Aug. 2014 - July 2015} \\ 
%Penn State Altoona, Altoona, PA \smallskip\smallskip\\
%{\bf Graduate Research/Teaching Assistant}, Department of Mathematics, \hfill {\em Aug. 2006 - May 2014} \\ 
%Southern Illinois University, Carbondale, IL \smallskip\smallskip\\
%{\bf Lecture}, Department of Physics, \hfill {\em Aug. 2004 - Jun. 2006} \\ 
%Beijing Nationality University, Beijing, China
%\end{rSection}
%
%




%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

%------------------------------------------------
\begin{rSubsection}{Investigator, MCCTR}{July 2017 - Present}{University of Mississippi Medical Center}{Jackson, MS}
\item[$\diamond$] \emph{Project: Uncovering and Understanding Population Differences with Topological Methods}\\
%- \emph{Mentors: Robert L. Hester, William A. Pruett, James G. Wilson}\\
%- Use mathematical modeling to study cardio-renal axis, duties included literature searches and reviews, extraction of differential-algebraic systems and validation; \\
- Developed a population creation toolkit for calibrating HumMod to given racial, gender, age, or fitness segments of a population. Modules include MCMC and measure based sampling algorithms, surrogate methodologies, and binned clustering algorithms.\\
- Realized a machine learning toolkit for deriving risk factors relative to a stipulated classifier.\\
- Created topological tools for analyzing large data sets, either model-derived or from clinical studies;
%- Reduce the number of proteins being used to refine the signal and minimize spurious connections; \\
%- Understand the mechanisms behind different etiologies of common comorbidities to obesity, and elucidate gaps in mechanistic understanding.
%\item[$\diamond$] 
\end{rSubsection}




%\begin{rSubsection}{Investigator, MCCTR}{July 2017 - Present}{University of Mississippi Medical Center}{Jackson, MS}
%\item[$\diamond$] Developing computational algorithms and database tools for cancer research in imaging and molecular
%biomakers for disease early detection, coding/non-coding genes regulation mechanisms and functional
%pathway networks study, translational discovery from in vitro experiment to caner patients genetic and
%clinical outcomes risk prediction
%\item[$\diamond$] Developing  high  throughput  computational  next  generation  sequencing  (NGS)  analysis  pipelines  for
%cancer  genomes  and  integrating  bio-omics  data  with  clinical  data  for  target  chemotherapy,  cancer
%subtypes prediction, and driver genes discovery.
%\item[$\diamond$] Developing  mathematical  methods  for  cardiovascular  disease  outcomes  (i.e.   heart  failure,  coronary
%heart disease, etc.)  risk factors prediction, genome wide association analysis, and genetic epidemiology
%study to find the genetic interaction with disease traits.
%\end{rSubsection}

%------------------------------------------------
\end{rSection}

%----------------------------------------------------------------------------------------
%	Position SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Teaching Experience}
\begin{rSubsection}{Assistant Professor of Mathematics}{August 2015 - Present}{Tougaloo College}{Tougaloo, MS}
\item[$\diamond$] MAT 103: College Algebra II, \hfill \emph{Fall 2015}
\item[$\diamond$] MAT 104: Trigonometry, \hfill \emph{Fall 2015, Spring 2016}
\item[$\diamond$] MAT 221: Calculus I, \hfill\emph{Fall 2015 - Spring 2020}
\item[$\diamond$] MAT 222: Calculus II, \hfill\emph{Fall 2016, Spring 2017}
\item[$\diamond$] MAT 321: Calculus III, \hfill\emph{Fall 2015, Fall 2016}
\item[$\diamond$] MAT 322: Calculus IV, \hfill\emph{Spring 2016 - 2020}
\item[$\diamond$] MAT 316: Differential Equations, \hfill\emph{Fall 2016 - 2019}
\item[$\diamond$] MAT 341: Linear Algebra, \hfill\emph{Spring 2017, Fall 2019}
\item[$\diamond$] MAT 414: Modern Algebra, \hfill\emph{Fall 2016, Fall 2017}
\item[$\diamond$] MAT 426: Advanced Calculus, \hfill\emph{Spring 2017, Fall 2018}
\item[$\diamond$] MAT 429: Complex Variable, \hfill\emph{Spring 2018}
\item[$\diamond$] MAT 434: Theory of Mathematical Statistics, \hfill\emph{Spring 2019, Spring 2020}
\item[$\diamond$] MAT 492: Senior Seminar, \hfill\emph{Spring 2019 - 2020}   
\end{rSubsection}


%------------------------------------------------



\begin{rSubsection}{Adjunct Biostatistics Professor}{January 2018 - Present}{Jackson Heart Study}{Jackson, MS}
\item[$\diamond$] MAT 208: Biostatistics, \hfill \emph{Spring 2018-2020}
%\item[$\diamond$] I shared the teaching duties for the biostatistics for Jackson Heart Study Scholar students. 
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Assistant Teaching Professor of Mathematics}{August 2014 - July 2015}{Penn State Altoona}{Altoona, PA}
\item[$\diamond$] Math 021: College Algebra I, \hfill\emph{Fall 2014}
\item[$\diamond$] Math 022: College Algebra II, \hfill\emph{Fall 2014, Spring 2015}
\item[$\diamond$] Math 211: Intermediate Cal. \& Diff. Eq., \hfill\emph{Summer 2015}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Graduate Teaching Assistant}{August 2006 - July 2014}{Southern Illinois University}{Carbondale, IL}
\item[$\diamond$] Math 101: Intro To Contemporary Math, \hfill\emph{Fall 2013}
\item[$\diamond$] Math 107: Intermediate Algebra, \hfill\emph{Spring 2012}
\item[$\diamond$] Math 109: Trig $\&$ Analytic Geometry, \hfill\emph{Summer 2013}
\item[$\diamond$] Math 140: Short Course in Calculus, \hfill\emph{Fall 2012, Spring 2014}
\end{rSubsection}


\end{rSection}


%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publication}

\begin{rSubsection}{}{}{}{}
\item[$\diamond$] Junqing Wang, \textbf{Xiuquan Wang}, Yixin Chen, Keli Xu, Yin-yuan Mo ,and Y. Zhou\\
          \emph{Comprehensive network analysis reveals alternative splicing-related lncRNAs in hepatocellular carcinoma}\\
          Under Review at Journal: Frontiers in Genetics, section Bioinformatics and Computational Biology
\item[$\diamond$] \textbf{X. Wang}, K. Xu, J. Wang and Y. Zhou\\
          \emph{LCLE: a web portal for comprehensive gene distance analysis for correlation networks in liver cancer}\\
          Under review at Genes
\item[$\diamond$] D. Xu, John.D. Reeve, \textbf{X. Wang}, and M. Xiao.\\
          \emph{Developmental variability and stability in continuous-time host-parasitoid models}\\
          Theoretical Population Biology. Vol. 78, No. 1, pp. 1-11, 2010.
\item[$\diamond$] John D. Reeve, \textbf{X. Wang}, M. Xiao, D. Xu, James T. Cronin.\\
          \emph{Insect Drift Movement Modeling and Parameter Estimations via Boundary Characteristics}\\
          Under review at Journal of Theoretical Biology
\item[$\diamond$] \textbf{X. Wang}, John D. Reeve, M. Xiao, D. Xu, James T. Cronin.\\
          \emph{Insect Biased Movement Modeling by the Mean First Passage Time to the Boundary}\\
          Under review at Journal of Mathematical Biology
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------



\begin{rSection}{Grants and Projects}

\begin{rSubsection}{}{}{}{}
\item[$\diamond$] NIH/NIGMS, MCCTR, Investigator Development \& Pilot Project\\
\emph{Title: Uncovering and Understanding Population Differences with Topological Methods}\\
Period: Jul. 2, 2017 - Jul. 1, 2020;\\ 
Total funding: 50\% release time plus \$12,225 pilot project funding;\\
Role: Principal Investigator
\item[$\diamond$] HHMI, Curriculum Development Award\\
\emph{Title: CRE course development for Introduction to Biological Research}\\
Period: Jul.1 - July 31, 2016; \\
Total funding: \$5000; \\
Role: Investigator
\item[$\diamond$] Penn State Altoona, Research Development Grant\\
\emph{Title: Insect biased Modeling and Parameter Estimation with Boundary Flux Approach inside Circle Habitat}\\
Period: Dec. 2015 - May 2016; \\
Total funding: \$3500; \\
Role: Principal Investigator
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Position SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Activities}

\begin{rSubsection}{Textbook Chapter Reviews}{}{}{}
\item[$\diamond$] Dirk Kroese, Zdravko Botev, Thomas Taimre and Slava Vaisman\\
\                 \emph{Mathematical and Staistical Methods for Data Science and Machine Learning}\\
                  Chapter 4-6: Unsupervised Learning, Regression, Regularization and Kernel Methods\\
               Statistics, Chapman \& Hall/CRC, Taylor \& Francis Group, April 21 2019
\end{rSubsection}

\begin{rSubsection}{Refereeing}{}{}{}
\item[$\diamond$] American Journal of Computational and Applied Mathematics
\item[$\diamond$] American Journal of Mathematics and Statistics
\item[$\diamond$] American Journal of Bioinformatics Research
\item[$\diamond$] Journal of Mechanical Engineering and Automation  
\item[$\diamond$] 2018 Second IFAC Conference on Modelling, Identification and Control of Nonlinear Systems.
\item[$\diamond$] 2017 SIAM Conference on Control and Its Applications (SIAM CT17)     
\item[$\diamond$] Nonlinear Analysis: Hybrid Systems
\item[$\diamond$] 1st IFAC Conference on Modelling, Identification and Control of Nonlinear Systems
\item[$\diamond$] The 9th World Congress on Intelligent Control and Automation       
\item[$\diamond$] The 9th IEEE International Conference on Control and Automation
\end{rSubsection}

\begin{rSubsection}{Selected Lectures}{}{}{}
\item[$\diamond$] \emph{Dimensional Reduction}, Ph.D Course, Department of Data Science\\
               University of Mississippi Medical Center, Jackson, MS, April 4\&9 2019
\item[$\diamond$] \emph{Introduction to Biological Research}, Undergraduate Course, Department of Biology\\
               Tougaloo College, Tougaloo, MS, Sep. 12-23 2016\\
%               \textbf{Course Development Award} from \textbf{HHMI} for developing this new
%course and new pedagogical techniques (e.g. video labs).
\end{rSubsection}

\begin{rSubsection}{Invited research seminars at colleges and universities}{}{}{}
\item[$\diamond$] \emph{Uncovering and Understanding Population Differences with Topological Methods}\\
               University of Mississippi Medical Center, MCCTR, Jackson, MS, May 7 2018
\item[$\diamond$] \emph{Insect Drift Movement Modeling and Parameter Estimations via Boundary Characteristics.}\\
               Belhaven University, Department of Mathematics, Jackson, MS, Apr. 14 2016
\end{rSubsection}

\begin{rSubsection}{Invited research presentations at conferences}{}{}{}
\item[$\diamond$] \emph{Uncovering and Understanding Population Differences with Topological Methods}\\
              Joint Mathematics Meetings: AMS Contributed Paper Session on General\\
              Denver, Colorado, Jan. 15, 2020.
\item[$\diamond$] \emph{Estimation of Diffusion Rate and Biased Movement Parameters with Mean Occupancy Time.}\\
              LA/MS Section - MAA, Annual Conference, Louisiana State University\\
              Shreveport, LA, Feb. 24-27, 2016.
\item[$\diamond$] \emph{Insect Drift Movement Modeling and Parameter Estimations via Boundary Characteristics.}\\
              Joint Mathematics Meetings: AMS Session on Mathematical Biology\\
              Seattle, WA, Jan. 6, 2016.
\end{rSubsection}


\begin{rSubsection}{Conference and Workshops Attended}{}{}{}
\item[$\diamond$] Interdisciplinary Curriculum Development Workshop, Tougaloo College, MS, May 16 - Jul. 27, 2016
\item[$\diamond$] Leadership Alliance Faculty Retreat on Mentoring Diverse Scholars, New York, NY, April 28 - 29, 2016
\item[$\diamond$] MAA Louisiana/Mississippi Section NExT Fellow, Professional Development Program, 2016 - 2017
\item[$\diamond$] 2018 Gulf States Math Alliance Conference,
Tulane University, New Orleans, LA, Feb. 23 - 25, 2018,  
\item[$\diamond$] Everything Disperses to Miami: The Role of Movement and Dispersal in Spatial Ecology, Epidemiology and Environmental Science (EDM),
Dec. 14 - 16, 2012.
\item[$\diamond$] Second Monterey Workshop on Computational Issues in Nonlinear Control, Nov. 7 - 8, 2011.
\item[$\diamond$] The Second International Conference on Mathematical Modeling and Analysis of Populations in Biological Systems, Oct. 9 - 11, 2009.\\
\emph{Poster: Dispersal Behavior with Biased Edge Movement Between Two Different Habitat Types}        
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Publication SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Services}

\begin{rSubsection}{Undergraduate Students Supervised}{}{}{}
\item[$\diamond$] \textbf{\em{Lajarius Black}}, B.S. in Mathematics and Computer Science \hfill {\em May. 2019} \\ 
\emph{Senior Paper: Application of Markov Chain Monte Carlo on Football Data}
\item[$\diamond$] \textbf{\emph{Jedda Carissa Alcee}}, B.S. in Mathematics \hfill {\em May. 2020} \\ 
\emph{Senior Paper: Visualizing Breast Cancer Data using t-SNE}   
\item[$\diamond$] \textbf{\emph{Dedrick Barkley}}, B.S. in Mathematics and Economics \hfill {\em May. 2020} \\ 
\emph{Senior Paper: Central Limit Theorem and its Application on Data Classification}
\item[$\diamond$] \textbf{\emph{GerMya Bradley}}, B.S. in Mathematics and Computer Science \hfill {\em May. 2020} \\ 
\emph{Senior Paper: Predicting  the  presence  of Alzheimer’s  using Artificial Intelligence}
\end{rSubsection}

\begin{rSubsection}{College Service}{}{}{}
        \item[$\diamond$] Faculty Mentor for Department of Mathematics, TC.
        \item[$\diamond$] Student Advisor for Department of Mathematics, TC.
        \item[$\diamond$] Student Advisor for the Mathematical Contest in Modeling (MCM), TC, 2017. 
        \item[$\diamond$] Attendance Policy Subcommittee, TC, 2018-2019
        \item[$\diamond$] Faculty Search Committee for Department of Mathematics, TC. 
        \item[$\diamond$] Committee to review and recommend approval of the 2017-2018 academic calendar, TC.
        \item[$\diamond$] Committee officer, College of Academic Affairs Council, 20TC, 16
        \item[$\diamond$] Committee at Center for Undergraduate Research, TC, 2015
        \item[$\diamond$] Committee Member, TC-MC Undergraduate Research Symposium, 2016, 2019                 
        \item[$\diamond$] Judge,\emph{Research Symposium on Students' Summer Research Series}, Science Fair at TC, 2015 - 2019
        \item[$\diamond$] Grader for Junior Math Competition, Penn State Altoona, 2014
        \item[$\diamond$] Judge, \emph{the annual Illinois Junior Academy of Science Region 8 Science Fair}, SIUC, 2012 - 2014.     
        \item[$\diamond$] Assistant, \emph{the annual Math Field Day organized by Department of Mathematics}, SIUC, 2011 - 2014.                        
\end{rSubsection}




\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Membership}

\begin{rSubsection}{}{}{}{}
\item[$\diamond$] American Mathematical Society (AMS)
\item[$\diamond$] Society for Industrial and Applied Mathematics (SIAM)
\item[$\diamond$] Society for Mathematical Biology (SMB)   
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}
%
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Coding & Mathematica, Python, R, Matlab, Stata \\
%ML  & linear and logistic regression (lasso, ridge, elasticnet), random forest, \\
%&gradient boosting (XGBoost), neural networks (RNNs), SVM, PCA, t-SNE,\\
%&graphical lasso, feature selection: L1, ensemble, mutual information based \\
%\end{tabular}
%
%\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\newpage
\begin{rSection}{References}

\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
Dr. William A Pruett (Project Mentor)               &  \\
Instructor, Department of Physiology   & \\
Scientist, Center for Computational Medicine                     &   \\ 
University of Mississippi Medical Center & \\
Email: wpruett@umc.edu&\\
\\
Dr. Mingqing Xiao (Ph.D advisor)                       &  \\
Professor, Department of Mathematics            &  \\
Southern Illinois University Carbondale      &  \\
Email: mxiao@siu.edu                  &  \\
\\
Dr. Wei Kang                         &  \\
Professor and Chair, Department of Applied Mathematics           &  \\
Naval Postgraduate School             & \\
Email: wkang@nps.edu                & \\
\\
Dr. Caixia Chen (Teaching)                        &    \\
Assistant Professor, Department of Mathematics and Computer Science                 &  \\
Tougaloo College                 & \\
Email: cchen1@tougaloo.edu       & \\
\end{tabular}

\end{rSection}









%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
